My title

### 2024-03-08 paper/paper.qmd
deleted model 1 cuz runtime too long

political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults1
#| tbl-cap: "Explanatory models Political Preferences (n = 40000)"
#| warning: false

modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )

@@

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences4
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences5
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences6
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences7
  ),
  statistic = "mad"
  )
```
```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences8
  ),
  statistic = "mad"
  )
```

>>>>

@@

@@

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences4
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences5
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences6
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences7
  ),
  statistic = "mad"
  )
```

```{r}
modelsummary(
  list(
    "Support Biden" = political_preferences8
  ),
  statistic = "mad"
  )
```
